\documentclass[letterpaper,11pt]{article}

\usepackage{geometry}
\usepackage{pslatex}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{color}
\usepackage{enumitem} % for ordered list labels
\usepackage{amssymb} % for symbols
\usepackage{scrextend} % for indentation
\usepackage{tabto} % for tabs
\usepackage{amsmath} % for text in equation
\usepackage{forest, tikz} % to make forest
\usepackage{mathtools}
\usepackage[ruled, lined, linesnumbered, commentsnumbered, longend]{algorithm2e}

\graphicspath{ {./} }
\geometry{ margin = 1.0in }

%%% TODO modify these variables %%%
\def\homeworknum{11}
\def\myname{Harshit Jain}
\def\myaccessid{hmj5262}
\def\myrecitation{8}
\def\lc{\left\lceil}   
\def\rc{\right\rceil}
%%%%

\pagestyle{fancy}
\lhead{{\bf CMPSC 465 Fall 2022}}
\chead{{\bf Assignment~\homeworknum}}
\rhead{{\bf \today}}

\newcounter{problemid}
%\stepcounter{problemid}
\def\newproblem{\clearpage\newpage{\bf Problem~\arabic{problemid}\stepcounter{problemid}}\hfill\fbox{\parbox{0.16\textwidth}{\bf Points:}}\par}

\setlength\parindent{0em}
\setlength\parskip{8pt}
\setlength{\fboxsep}{6pt}


\begin{document}

\framebox[\textwidth]{
	\parbox{0.96\textwidth}{
		\parbox{0.12\textwidth}{\bf Name:}\parbox{0.6\textwidth}{\myname}\\
		\parbox{0.12\textwidth}{\bf Access ID:}\parbox{0.6\textwidth}{\myaccessid}\\
		\parbox{0.12\textwidth}{\bf Recitation:}\parbox{0.6\textwidth}{\myrecitation}
	}
}


%% your solutions %%%

\newproblem
\textbf{Acknowledgements}
\begin{enumerate}[label=(\alph*)]
    \item I worked with Yug Jarodiya.
    \item I did not consult with anyone in my group members.
    \item I did not consult any non-class materials.
\end{enumerate}


% PROBLEM 1
\newproblem
\begin{enumerate}[label=(\alph*)]
    \item \underline{Objective Function:}

    Let $x_{ij}$ be a variable representing whether client $i$ is served by server $j$. So, $x_{ij} = 0$ or $1$. The objective function is to minimize the total service cost, which is the sum of the service costs over all clients for the optimal solution. It is represented as: \[ \text{maximize }\sum_{i \in C} \sum_{j \in S} c_{ij} x_{ij}\].

    \underline{Constraints:}

    \begin{itemize}
        \item Each client must be served by at least one server, which can be represented as: \[\sum_{j \in S} (x_{ij} \geq 1) \forall i \in C\].
        \item At most, $k$ servers can be functional at a time, which can be represented as: \[\sum_{j \in S} (x_{ij} \leq k) \forall i \in C\].
        \item The variable $x_{ij}$ can only take the values $0$ or $1$, which can be represented as: \[0 \leq x_{ij} \leq 1 \forall i \in C, j \in S\].
    \end{itemize}
    
    \item \underline{Objective Function:}
    
    Let $y_i$ be continous variable representing the amount of service cost that must be provided to client $i$. The objective function is to maximize the total amount of service cost that can be provided to the clients, which can be represented as: \[ \text{maximize} \sum_{i \in C} y_i \]

    \underline{Constraints:}

    \begin{itemize}
        \item The amount of service cost provided to each client must eb less than or equal to the service cost of the corresponding server, which can be represented as: \[y_i \leq c_{ij} \forall i \in C, j \in S\]
        \item The total amount of service cost provided to all clients must be less than or equal to the total amount of service cost that can be provided by the $k$ servers, which can be represented as: \[(\sum_{i \in C} y_i) \leq (\sum_{j \in S} c_{ij}) \forall i \in C, j \in S\]
        \item The continous variable $y_i$ must be non-negative which can be represented as: \[y_i \geq 0 \forall i \in C\]
    \end{itemize}
\end{enumerate}


% PROBLEM 2
\newproblem

maximize $\Rightarrow$ $2x_1 + 7x_2 + x_3$

subject to $\Rightarrow$ $x_1 - x_3 = 7$

\tabto{58pt} $3x_1 + x_2 \geq 24$

\tabto{58pt} $x_2 \geq 0$

\tabto{58pt} $x_3 \leq 0$

Here, ($x_1 - x_3 = 7$) will undergo equality to inequality which in turn make the constraints as ($x_1 - x_3 \leq 7$) and ($x_1 - x_3 \geq 7$).

Now, ($x_1 - x_3 \geq 7$), ($3x_1 + x_2 \geq 24$) and ($x_3 \leq 0$) has the wrong inequality direction so we will multiple both sides by $-1$ to change the inequality which results into ($x_3 - x_1 \leq -7$), ($-3x_1 - x_2 \leq -24$), and ($-x_3 \geq 0$) (non-negative constraint).

Here, non-negative constraint of $x_1$ is missing. So, $x_1 \geq 0$, $x_1 \leq 0$. We want to combine these two constraints in a way that we can enforce both these conditions together. We will rewrite $x_1 = x_1^{+} - x_1^{-}$ in all the above equations.

\underline{Final answer:}

maximize $\Rightarrow$ $2(x_1^{+} - x_1^{-}) + 7x_2 + x_3$

subject to $\Rightarrow$ $(x_1^{+} - x_1^{-}) - x_3 \leq 7$

\tabto{58pt} $x_3 - (x_1^{+} - x_1^{-}) \leq -7$

\tabto{58pt} $(-3)(x_1^{+} - x_1^{-}) - x_2 \leq -24$

\tabto{58pt} $x_2 \geq 0$

\tabto{58pt} $(-x_3) \geq 0$

\tabto{58pt} $x_1^{+} \geq 0$

\tabto{58pt} $x_1^{-} \geq 0$

According to Standard form $1$:

maximize $\Rightarrow$
$
    \begin{bmatrix}
        2 & -2 & 7 & 1
    \end{bmatrix}
       \times
    \begin{bmatrix}
       x_1^{+}\\
       x_1^{-}\\
       x_2\\
       x_3
    \end{bmatrix}
$

Subject to $\Rightarrow$
$
    \begin{pmatrix}
        1 & -1 & 0 & -1\\ 
        -1 & 1 & 0 & 1\\
        -3 & 3 & -1 & 0
    \end{pmatrix}
    \times
    \begin{pmatrix}
        x_1^{+}\\
        x_1^{-}\\
        x_2\\
        x_3
    \end{pmatrix}
    =
    \begin{pmatrix}
        7\\ 
        -7\\
        -24
    \end{pmatrix}
$

\tabto{63pt} $x_1^{+}$, $x_1^{-}$, $x_2$, $-x_3 \geq 0$
\end{document} 